|

### 2019-07-15 appendix/appendix-institutional-design-climate-policy.Rmd
small edits to the appendix

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, [danilofreire@brown.edu](mailto:danilo_freire@brown.edu), <http://danilofreire.github.io>. Corresponding author.

@@

# AMCE (Average Marginal Component Effect) Estimator

>>>>

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>. Corresponding author.

@@

# Average Marginal Component Effect (AMCE) Estimator
